---
title: "ps_7"
author: "Connor Riordan"
date: "4/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(stringr)
library(readr)
library(janitor)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(stringr)
library(skimr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(tidyr)
library(broom)
library(gt)
```

## 1A

```{r, chunk_1A, echo = FALSE}

# I read in the csv so I would have my dataset!

government <- read.csv("data_directory/HSall_members.csv") %>%
  clean_names()

# At first, I solved this problem without filtering for congress == 116, and
# I was so confused as to why some of my code later on wasn't working. However,
# I eventually figured that out. For mutate, I thought a series of ifelse 
# statements would be best for coming up with the different parties (when
# applicable). Then, it was easy to use age, and skimming and printing was
# very intuitive.

g <- government %>%
  filter(congress == 116) %>%
  filter(chamber == "Senate" | chamber == "House") %>%
  mutate(party = ifelse(party_code == 200, "Republican",
                        ifelse(party_code == 100, "Democrat", 
                               ifelse(party_code == 328, "Independent", "N/A")))) %>%
  filter(!party == "Independent") %>%
  mutate(age = 2019-born) %>%
  mutate(nominate_percentile = 100 *percent_rank(nominate_dim1))

g %>%
  skim(nominate_percentile, age) %>%
  print()

```

## 1B

```{r, chunk_1B, echo = FALSE, results = 'hide'}

# I decided to make it so that I could examine both the entire distribution
# for both parties for age, as well as setting fill to party so I could also
# see how they each stack up against one another.

g %>%
  ggplot(aes(age, fill = party)) + geom_histogram(bins = 30, color = "black") +
  theme_bw() + labs(
    title = "Distribution of Congressional Ages",
    x = "Age",
    y = "Count"
  ) + scale_fill_manual(values = c("blue", "red")) %>%
  print()

# Much like the graph above, I thought it would be best to have a way to
# examine the entire dataset and then see how it was divided by chamber, which
# was very illuminating.

g %>%
  ggplot(aes(nominate_percentile, fill = chamber)) + geom_histogram(bins = 30, color = "black") +
  theme_bw() + labs(
    title = "Distribution of DW Nomination Percentiles",
    x = "Nomination Percentile",
    y = "Count"
  ) + scale_fill_manual(values = c("sky blue", "pink")) %>%
  print()

```

## 1C

```{r, chunk_1C, echo = FALSE}

# For this problem, I just needed to use summarize and cor to find my desired
# value.

g %>%
  summarize(correlation = cor(age, nominate_percentile)) %>%
  print()

# A negative coefficient would indicate that as age increases, the DW
# Nomination Percentile decreases.




```

## 1D

```{r, chunk_1D, echo = FALSE, results = 'hide'}

# When I originally made this plot, I couldn't figure out why my black
# regression wasn't showing up on the graph. I was using two geom_smooth()
# functions, which I thought was right, but apparently I was wrong. Except...
# I wasn't. I just had the wrong code intside the smooth functions; I was
# missing color = "black" in my first, and after fixing that I was able to
# produce the plot below.

scatterplot <- g %>%
  ggplot(aes(age, nominate_percentile, color = party)) + geom_point() + 
  geom_smooth(method = "glm", se = FALSE, color = "black") + 
  geom_smooth(method = "glm", se = FALSE) + 
  scale_color_manual(values = c("blue", "red")) + labs(
    title = "Relationship Between Age and DW Nominate Percentile",
    subtitle = "Higher scores represent more conservative positions",
    x = "Age",
    y = "Percentile Rank (DW Nominee)",
    color = "Party"
  ) + theme_classic()

scatterplot

```

## 2A

```{r, chunk_2A, echo = FALSE}

# To solve this problem, I first filtered by democrats, and I pretty much
# used the book to help me complete this problem. I knew I needed to do
# nominate_percentile ~ age as well as tidy and select. Inside select I had
# to add in term to what was already stated in the book. After that...
# my old friend gt()! How I missed him.  It was simple and fun to figure out 
# all the labeling for the table.

g %>%
  filter(party_code == 100) %>%
  lm(formula = nominate_percentile ~ age, .) %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  gt() %>%
  tab_header(
    title = "Effect of Age on DW Nominate Percentile",
    subtitle = "Higher percentile suggests more conservative"
  ) %>% 
  cols_label(
    term = "Varibale",
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Upper Bound"
  )

```

## 2B

The estimated average treatment effect for this data is -0.3322965. What this means is that as age increases by one, the DW Nominate Percentile will go down by 0.3322965. We shouldn't necessarily think of this relationship as causal because there are a multitude of reasons why older democratic congressmen might be less conservative. One example could be that older democratic congressmen have witnessed republican and democratic administrations and have felt liberal ideas best suited the country, whereas new democrats have to appeal to more moderate voters. We calculated a confidence interval around the estimated average treatment so we can confidently say that the true value for how age affects the DW Nominate Percentile lies in between the upper and lower bounds.

## 2C

The causal effect of x, or military treatment, on y, the DW nominate percentile, is the difference in the potential outcomes of y given different values of x. We can take the mean of all causal effects to find the estimated average treatment, which tells us that serving in the military will change a congressman's DW nominate percentile by (+ or -) that amount. While randomization offers a close approximation of the ATE, this isn't a causal relationship because we can only observe one potential outcome and can never know what it would be if the congressman received the other.

## 3

```{r, chunk_Q3, echo = FALSE, results = 'hide'}

# For this first chunk of code, I was in Emily's study hall for well past when
# it ended because I didn't have the correct values on the y-axis. We both
# couldn't figure out why for the longest time - all of my code was correct
# (or so we thought). What ended up being the case was my mutate for
# nominate_percentile was two rows of code above where it should have been, and
# I hadn't filtered for the correct data before it ran. After we fixed that,
# the plot came out exactly as we needed it to. I had originally created a
# year column in order to solve for age, but then I realized I didn't need to
# and could just put the whole equation right into the mutate. The second piece
# of code followed exactly what the textbook told us to do, and I knew for
# upper and lower I needed to use 1.96 for the 95% confidence interval. The
# final piece - ggplot - was very easy, and I am just so relieved I have the
# right values on the y-axis now.

democrat <- government %>%
  mutate(age = (1787 + (congress*2))-born) %>%
  filter(party_code == 100) %>%
  filter(chamber == "Senate" | chamber == "House") %>%
  mutate(nominate_percentile = 100 * percent_rank(nominate_dim1)) %>%
  group_by(congress) %>%
  nest()

democrat <- democrat %>%
  mutate(mod = map(data, ~ lm(nominate_percentile ~ age, data = .)),
         reg_results = map(mod, ~ tidy(.)),
         coef = map_dbl(reg_results, ~ filter(., term == "age") %>% pull(estimate)),
         se = map_dbl(reg_results, ~ filter(., term == "age") %>% pull(std.error)),
         upper = coef + (1.96 * se),
         lower = coef - (1.96 * se))
  
democrat %>%
  ggplot(aes(x = congress, y = coef)) + geom_point(color = "blue") + 
  geom_errorbar(aes(x = congress, ymin = lower, ymax = upper), color = "blue") +
  theme_classic() + labs(
    title = "Average Treatment Effect of Age on Conservativism
    Among Democrats Over Time",
    subtitle = "Scores use DW Nominate Dimension 1
    95% Confidence Interval",
    x = "Congress",
    y = "Estimate"
  )
  
```











